Dish: Distribution-oblivious Shell Scripting

### 2019-11-23 pldi/draft.tex

\noindent
\TODO{Change that with the new splitter}
On the other hand, given an input file \verb|in| that is a FIFO pipe,
and two output files \verb|out1, out2| the first of which is bounded
to \verb|N| lines, a 2-splitter can be implemented as:

\begin{lstlisting}[language=sh, float=h, numbers=none]
 head -n $N $in > $out1 ; cat $in > $out2
\end{lstlisting}

>>>>

\noindent
On the other hand, given an input file \verb|in| that is a FIFO pipe,
and two output files \verb|out1, out2| the first of which is bounded
to \verb|N| lines, a 2-splitter can be implemented as:

\begin{lstlisting}[language=sh, float=h, numbers=none]
  tee >(head -n $N > $temp1;
        dd of=/dev/null > /dev/null 2>&1 &
        cat $temp1 > $out1) |
       (tail -n +${N+1} > $out2;
        dd of=/dev/null > /dev/null 2>&1)
\end{lstlisting}
 %% head -n $N $in > $out1 ; cat $in > $out2
